ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-28 pyked.tex
fix for minted formatting

The \pybox{DataPoint} class has two instance methods defined, called
\pybox{get_cantera_mole_fraction()} and \pybox{get_cantera_mass_fraction()}.
With these methods, the composition of the reactant mixture can be output to a
format that can be used to set the composition of a Cantera \pybox{Solution}.
Note that the \pybox{composition} specification does not contain the molecular
weights of the components, so conversion between mole fractions and mass
fractions is not possible.

The \pybox{ChemKED} class has one instance method defined, called
\pybox{get_dataframe()}. Using this method, the user can get an instance of a
Pandas~\autocite{pandas} \pybox{DataFrame} that contains the information in the
list of \pybox{DataPoint}s. The user can specify the columns included in the
\pybox{DataFrame} by passing a list of column names to the
\pybox{output_columns} argument of the \pybox{get_dataframe()} method. The
possible columns are not case-sensitive and are:

>>>>

The \pybox{DataPoint} class has two instance methods defined, called
\pybox{get_cantera_mole_fraction()} and \pybox{get_cantera_mass_fraction()}.
With these methods, the composition of the reactant mixture can be output to a
format that can be used to set the composition of a Cantera~\pybox{Solution}.
Note that the \pybox{composition} specification does not contain the molecular
weights of the components, so conversion between mole fractions and mass
fractions is not possible.

The \pybox{ChemKED} class has one instance method defined:
\pybox{get_dataframe()}. Using this method, the user can get an instance of a
Pandas~\autocite{pandas} \pybox{DataFrame} that contains the information in the
list of \pybox{DataPoint}s. The user can specify the columns included in the
\pybox{DataFrame} by passing a list of column names to the
\pybox{output_columns} argument of the \pybox{get_dataframe()} method. The
possible columns are not case-sensitive and are:
